Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-09-27 document/submission/ms.tex
Submitted version of the paper.

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin R. Covey,\altaffilmark{5} J.F. Donati,\altaffilmark{6,7} Silvia H. P. Alencar,\altaffilmark{8} Gaitee A.J. Hussain,\altaffilmark{9,10} Benjamin J. Shappee,\altaffilmark{11,12} Gregory N. Mace,\altaffilmark{13} Jae-Joon Lee\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}

@@

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply 
%a consistently large ($>50\%$) fill factors across all IGRINS spectral orders, with 
a best fit filling factor of $f\sim80$\% starspots at the time of the observation. These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time. A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation. The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.98\textwidth]{figures/LkCa4_phot1986-2016.pdf}
 \caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.  The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DBSP, and TripleSpec.  The near contemporaneous DBSP and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.  The abscissa range is equal to the current lifespan of the first author of this paper.}
 \label{fig:PhotTime}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{figures/Vband_22s.pdf}
 \caption{Phase-folded lightcurves constructed assuming $P=3.375$ days for all 22 observing seasons.  The blue solid lines show a ``multiterm'' regularized periodic fit, that is, keeping the first $M_{\rm max}=4$ Fourier components \citep{vanderplas15a}.  The vertical lines show the epochs at which spectra or ancillary photometry were obtained, with the same line styles and colors as Figure \ref{fig:PhotTime}.  LkCa 4 shows secular changess in its light curve morphology.  The IGRINS spectrum was acquired near the median flux level, not the extrema.}
 \label{fig:PhotPhase}
\end{figure*}

@@

\input{tables/tbl_estV_atObsEpoch.tex}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.48\textwidth]{figures/single_Teff_v_order}
 \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.  The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.  The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.  The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
 \label{fig:SingleTeffvsOrder}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_04} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_01} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_05} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_06} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_02} 
 \includegraphics[width=0.45\textwidth]{figures/spectral_postage_stamp_03} 
 \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).  The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.  The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
 \label{fig:specPostageStamp}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{figures/violin_Teff_fill_order} 
 \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).  The stellar parameters are derived independently in each spectral order.  Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
 \label{fig:TwoTempResults}
\end{figure*}

@@

\input{tables/tbl_best_fit.tex}

@@

\begin{figure}
 \centering
 \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{figures/phot_2750}
\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
\label{fig:sed}
\end{figure}

\begin{figure*}
 \centering
 \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{figures/lores_panels_2750k}
 \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).  The inset shows that the 2750 K (red, 80\% fill factor) and 4100 K (blue, 20\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.  The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum. Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere (red), and the two temperature photosphere (pink) that best fits the IGRINS spectrum.  The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.  Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.  Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.  The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
 \label{fig:lores}
\end{figure*}

\begin{figure}
 \centering
 %\includegraphics[width=0.65\textwidth]{}
% \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{figures/jbandjump}
\includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.48\textwidth]{figures/jbandjump}
\caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.  The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.  The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.  The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption. }
 \label{fig:h2ojump}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{figures/vband_spot_2750k}
\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.  The optical brightness depends mostly on the hot component.  If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.  The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\Delta V=0.6$. }
\label{fig:vband_spot}
\end{figure*}
%\todo{Update with all available photometry or the derived multi-term fit}

\begin{figure*}
 \centering
 \begin{tabular}{ll}
 \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{figures/bv_pec13} 
    &
   \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{figures/vr_pec13}
    \end{tabular}
\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions.  The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
\label{fig:colors}
\end{figure*}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{figures/lkca4_tio_forpaper}
 \caption{Variability in TiO bands measured with ESPaDOnS.  The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.  The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
 \label{fig:tiovar}
\end{figure*}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{figures/lkca4_hrdiag_paper2}
 \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.  The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.  The yellow shaded region corresponds to the range of apparent effective temperatures that are would be measured as the hot component rotates into and out of our view.  The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
 \label{fig:hrdiag}
\end{figure*}

@@

\begin{figure}
 \centering
\includegraphics[width=0.45\textwidth]{figures/v_v-r_Grankin} 
\caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.  The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5). In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.}
 \label{fig:grankin_vr}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{figures/H_band_spectra_3x7}
 \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelenth decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.  The $y-$axis is on a logarithmic scale.  The red line is the cool photosphere while the blue line is the hot photosphere.  The purple line is the composite mixture model.}
 \label{fig:Hband3x7}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{figures/K_band_spectra_3x7}
 \caption{IGRINS Orders $93-73$, with the same layout, ordering, and colors as Figure \ref{fig:Hband3x7}. The $y-$axis is on a logarithmic scale.}
 \label{fig:Kband3x7}
\end{figure*}

@@

Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
\LongTables
\input{tables/tbl_order_results.tex}

@@

Table \ref{tbl_history} lists measurements of \name from previous studies, compared to this work.
\input{tables/tbl_history.tex}

>>>>

\author{Michael A. Gully-Santiago,\altaffilmark{1} Gregory J. Herczeg,\altaffilmark{1} Ian Czekala,\altaffilmark{2} Garrett Somers,\altaffilmark{3} Konstantin Grankin,\altaffilmark{4} Kevin R. Covey,\altaffilmark{5} J.F. Donati,\altaffilmark{6,7} Silvia H. P. Alencar,\altaffilmark{8} Gaitee A.J. Hussain,\altaffilmark{9,10} Benjamin J. Shappee,\altaffilmark{11,12} Gregory N. Mace,\altaffilmark{13} Jae-Joon Lee,\altaffilmark{14} T.~W.-S.~Holoien,\altaffilmark{15,16} Jessy Jose,\altaffilmark{1} Chun-Fan Liu\altaffilmark{17,1}}

@@

Ages and masses of young stars are often estimated by comparing their observed luminosities and effective temperatures to pre-main sequence stellar evolutionary model tracks, but nonstandard physics like magnetic fields and starspots complicate this process. In order to understand their influence, we study in detail the heavily-spotted weak-lined \emph{T-Tauri} star LkCa 4 by searching for spectral signatures of radiation originating from the starspot or starspot groups.  We introduce a new methodology for constraining both the starspot filling factor and the typical spot temperature by fitting two-temperature stellar atmosphere models constructed from \PHOENIX\ synthetic spectra to a high-resolution near-IR IGRINS spectrum.  Spectral features are attributable to both an ambient photosphere $\teffa\sim4100$ K and to cool starspots $\teffb\sim2700-3000$ K, which imply a best fit filling factor of $f\sim80$\% starspots at the time of the observation. These results are bolstered by the spectral energy distribution, color variability, TiO variability, rotational modulation, and low-resolution optical/IR spectroscopy, which collectively support the picture of an extremely heavily spotted star with secularly changing starspot filling factors and temperature contrasts through time. A persistent hotspot covering $\sim20$\% of the surface is a plausible alternative explanation. The revised effective temperature and luminosity make LkCa 4 appear much younger and lower mass when compared to previous measurements, a bias likely afflicting most young, heavily spotted stars, and which likely contribute to uncertainties in open cluster ages inferred from low-mass stars and in large age spreads of those clusters. We also discuss the detailed influence of starspots on the IGRINS spectrum, which in some regions acts as a relatively featureless ``veiling'' continuum owing to the large rotational broadening ($\vsini\sim28$ km~s$^{-1}$) and heavy line-blanketing in cool star spectra.

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.98\textwidth]{LkCa4_phot1986-2016.pdf}
 \caption{Overview of \name $V-$band photometric monitoring from 1986$-$2016.  The vertical lines denote the observing epochs of 2MASS, IGRINS, ESPaDOnS, DBSP, and TripleSpec.  The near contemporaneous DBSP and TripleSpec epochs lay on top of each other on this scale, as do the 12 ESPaDOnS epochs.  The abscissa range is equal to the current lifespan of the first author of this paper.}
 \label{fig:PhotTime}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{Vband_22s.pdf}
 \caption{Phase-folded lightcurves constructed assuming $P=3.375$ days for all 22 observing seasons.  The blue solid lines show a ``multiterm'' regularized periodic fit, that is, keeping the first $M_{\rm max}=4$ Fourier components \citep{vanderplas15a}.  The vertical lines show the epochs at which spectra or ancillary photometry were obtained, with the same line styles and colors as Figure \ref{fig:PhotTime}.  LkCa 4 shows secular changess in its light curve morphology.  The IGRINS spectrum was acquired near the median flux level, not the extrema.}
 \label{fig:PhotPhase}
\end{figure*}

@@

\input{tbl_estV_atObsEpoch.tex}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.48\textwidth]{single_Teff_v_order}
 \caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum and assuming a single component photosphere.  The effective temperature derived in the $K-$band is about 800 K lower than that derived in optical.  The increasing flux density from starspots compared to the flux from ambient photosphere can explain the observed trend in derived $\teff$.  The cluster of $H-$band orders at 1.7 $\mu$m correspond to a local peak in flux density of cool starspots.}
 \label{fig:SingleTeffvsOrder}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_04} 
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_01} 
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_05} 
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_06} 
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_02} 
 \includegraphics[width=0.45\textwidth]{spectral_postage_stamp_03} 
 \caption{Examples of spectral features in the observed IGRINS spectrum (light gray line).  The composite spectrum model (purple thin line) is consistent with the observed spectrum for a range of fill factors, with examples of the median fill factor (middle panel of triptych) and $\pm2\sigma$ fill factors demarcated on the spectral postage stamps.  The upper right triptych shows a Zeeman-sensitive Mg I line that is modeled with no special attention to magnetic field, but is still coarsely reproduced in its gross appearance as a function of temperature, but potentially biasing estimates of $\teffa$ and/or $f_{\Omega}$ for individual spectral orders.}
 \label{fig:specPostageStamp}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{violin_Teff_fill_order} 
 \caption{Marginal probability distributions mirrored through the vertical axis \citep[``Violin plot'']{waskom14} for 48 IGRINS orders for $\teffa$ (blue shade), $\teffb$ (red shade), and fill factor $f_{\Omega}$ (yellow shade).  The stellar parameters are derived independently in each spectral order.  Spectral orders show differing levels of constraint on the starspot and ambient photosphere properties, with some ($o=104, 102, 100, 88, 83$) showing tight constraints on the filling factor of starspots.  The starspot temperature is consistent with values even lower than 2700 K, the lower limit of the temperature range used.  $K-$band orders show lower estimates for the ambient photosphere, though many of these estimates are unreliable due to spectral line outliers and uncorrected telluric residuals (light shaded distributions).}
 \label{fig:TwoTempResults}
\end{figure*}

@@

\input{tbl_best_fit.tex}

@@

\begin{figure}
 \centering
 \includegraphics[trim=3.1cm 13cm 1.0cm 3.6cm, clip=true, width=0.49\textwidth]{phot_2750}
\caption{The SED of LkCa 4 (red) compared with the two-temperature spectrum obtained from the best fit to the IGRINS spectra (black).}
\label{fig:sed}
\end{figure}

\begin{figure*}
 \centering
 \includegraphics[trim=2.1cm 3.0cm 1cm 7.7cm, clip=true, width=0.70\textwidth]{lores_panels_2750k}
 \caption{Top:  The low-resolution optical/near-IR spectrum of LkCa 4 obtained from Palomar/DBSP and APO/Triplespec on 30 December 2008 (black), compared to a synthetic spectrum of a two temperature photosphere (purple).  The inset shows that the 2750 K (red, 80\% fill factor) and 4100 K (blue, 20\% fill factor) components contribute equally to the near-IR spectrum, but the 4100 K component dominates the blue emission.  The synthetic spectrum is reddened by $A_V=0.4$ mag and scaled to the observed $J$-band spectrum. Bottom:  The low-resolution optical (left) and near-IR (right) spectrum of LkCa 4, compared with a 3900 K photosphere (blue), a 3500 K photosphere (red), and the two temperature photosphere (pink) that best fits the IGRINS spectrum.  The synthetic spectra are scaled separately to the optical spectrum at 0.75 $\mu$m and to the near-IR spectrum at 1.5 $\mu$m.  Warm photospheres accurately reproduce molecular bands at $0.7$ $\mu$m but fail to fit the spectral features at longer wavelengths.  Cooler photospheres predict molecular bands at $<0.7$ $\mu$m that are much deeper than observed.  The two temperature photosphere accurately fits spectral features in the optical and near-IR.}
 \label{fig:lores}
\end{figure*}

\begin{figure}
 \centering
 %\includegraphics[width=0.65\textwidth]{}
% \includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.65\textwidth]{jbandjump}
\includegraphics[trim=2.6cm 13.0cm 2.3cm 2.5cm, clip=true, width=0.48\textwidth]{jbandjump}
\caption{The constraint on the size and temperature of the cool spot from the H$_2$O absorption band depth between $J$ and $H$-bands.  The contours show the flux ratio between 1.30 and 1.34 $\mu$m (shaded yellow region in inset plot), as produced by the Phoenix models.  The solid and hatched purple lines show the best fit and range of acceptable contours from the APO/TripleSpec spectrum, which was obtained when the cool spot fraction was $\sim 84$\%.  The range of acceptable contour is based on an estimate uncertainty of $\sim 2$\% in observed flux ratio, which is dominated by uncertainty in telluric correction of strong H$_2$O absorption. }
 \label{fig:h2ojump}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=1.6cm 12.6cm 2.2cm 2.4cm, clip=true, width=0.60\textwidth]{vband_spot_2750k}
\caption{The $V$-band magnitude in 2014--2015, converted into fill factor for the cool component.  The optical brightness depends mostly on the hot component.  If we fix a 75\% filling factor, as measured in the IGRINS spectrum, to $V=12.83$ at the time of the observation, then the $V$-band amplitude  corresponds to filling factors of 67--83\%.  The factor of $\sim 2$ change in visible surface area of the hot component, from 33\% to 17\%, is required to produce the $\Delta V=0.6$. }
\label{fig:vband_spot}
\end{figure*}
%\todo{Update with all available photometry or the derived multi-term fit}

\begin{figure*}
 \centering
 \begin{tabular}{ll}
 \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.2cm, clip=true, width=0.45\textwidth]{bv_pec13} 
    &
   \includegraphics[trim=2.6cm 13.0cm 2.8cm 2.2cm, clip=true, width=0.45\textwidth]{vr_pec13}
    \end{tabular}
\caption{The observed optical colors of LkCa 4 from \citet{grankin08}, compared with predictions.  The model is constructed instead by converting $V$-band brightness to a cool spot filling factor and subsequently calculating colors from main sequence colors and bolometric corrections of \citet{pecaut13} (purple lines).}
\label{fig:colors}
\end{figure*}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=3.2cm 4.0cm 2.6cm 8.3cm, clip=true, width=0.65\textwidth]{lkca4_tio_forpaper}
 \caption{Variability in TiO bands measured with ESPaDOnS.  The $V-$band emission is estimated from fits to the ASAS-SN lightcurve obtained during the same period.  The bottom left panel shows a correlation between $V-$band magnitude and the TiO-7140 index, while the bottom right shows a similar correlation with the average of the TiO 6200, CaH 6800, and TiO 7600 indices.}
 \label{fig:tiovar}
\end{figure*}

@@

\begin{figure*}
 \centering
 \includegraphics[trim=2.6cm 13.0cm 2.8cm 3.5cm, clip=true, width=0.65\textwidth]{lkca4_hrdiag_paper2}
 \caption{Locations for LkCa 4 on an HR diagram, compared with models of pre-main sequence evolution calculated by \citet{baraffe15} with isochrones (black lines) and evolution models of a single mass (dashed blue lines) as marked.  The measured effective temperature and luminosity from this paper, based on the two-component fit and a median $V$-band magnitude, corresponds to the black asterisk.  The yellow shaded region corresponds to the range of apparent effective temperatures that are would be measured as the hot component rotates into and out of our view.  The blue circle corresponds to the measurement at blue-optical wavelengths by \citet{donati14}, the purple square corresponds to the measurement from low-resolution optical spectra, biased to TiO band strengths, by \citet[][biased to]{herczeg14}, while the red diamond corresponds to what we would measure from the K-band spectrum and 2MASS $J$-band magnitude.}
 \label{fig:hrdiag}
\end{figure*}

@@

\begin{figure}
 \centering
\includegraphics[width=0.45\textwidth]{v_v-r_Grankin} 
\caption{Grey points are all \citet{grankin08} photometric data, while black points are the subset of observations from the 1999 season.  The purple line represents a two component photometric model  described by \citet{grankin08}, comprising a photospheric temperature of 4040K (for K7), and a temperature of spotted area of 3030K (for an M5). In this model, the spot coverage of the observed hemisphere varies from $\sim36\%$ at maximum brightness, and $\sim82\%$ at minimum brightness.}
 \label{fig:grankin_vr}
\end{figure}

@@

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{H_band_spectra_3x7}
 \caption{IGRINS Orders $122-100$, with panels arranged with the shortest wavelength in the upper left corner with central wavelenth decreasing toward the bottom of the leftmost column, then decreasing through the subsequent columns.  The $y-$axis is on a logarithmic scale.  The red line is the cool photosphere while the blue line is the hot photosphere.  The purple line is the composite mixture model.}
 \label{fig:Hband3x7}
\end{figure*}

\begin{figure*}
 \centering
 \includegraphics[width=0.95\textwidth]{K_band_spectra_3x7}
 \caption{IGRINS Orders $93-73$, with the same layout, ordering, and colors as Figure \ref{fig:Hband3x7}. The $y-$axis is on a logarithmic scale.}
 \label{fig:Kband3x7}
\end{figure*}

@@

Table \ref{tbl_order_results} lists all the IGRINS spectral order results.
\LongTables
\input{tbl_order_results.tex}

@@

Table \ref{tbl_history} lists measurements of \name from previous studies, compared to this work.
\input{tbl_history.tex}
